---
title: "onRobs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{onRobs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, echo=FALSE}
knitr::opts_chunk$set(
	message = TRUE,
	warning = FALSE,
	include = FALSE
)
#library(onRobS)
```


This package on R OBS (pronounce on air OBS) enables you to control OBS through the OBS Websockets Server using R functions.
Its strongly rely on the *websocket* package.

### OBS Websocket Server in OBS

OBS must be running (the package has been tested with version 29) and you need to start the websockets server. obs-websocket is  included by default with OBS Studio since version 28.0.0. Previous version were relying on a plugin.

You will find the websocket server in **Tools > Websockets server Settings**

Make sure to tick the *"Enable WebSockets server"* check box and if you want to use authentication (strongly encouraged), also tick the *"Enable authentication"* checkbox and choose a password.

For more detailed information about OBS websockets, you can read the [obs-websocket 5.1.0 Protocol](https://github.com/obsproject/obs-websocket/blob/release/5.2.3/docs/generated/protocol.md)

## Installation

You can install the development version of onRobs from [GitHub](https://github.com/franklentz/onRobs) with:

``` r
# install.packages("devtools")
devtools::install_github("franklentz/onRobs")
```


### Connection and Identification

There are three steps to start interacting with OBS Webserver once it is running

- Create an OBSWebsocket (this is the object you will use to interact with OBS through the websockets server
- Establish a connection with the server
- Identify and authenticate. If authentication has been activated on the OBS Websockets server, you will need to supply the password

```
library(onRobs)
myobs <- createOBSWebsocket() 
connectToOBS(obs = myobs)
identifyToOBS(obs = myobs, eventSub = "33", password = "myObsWebsocketsServerPassword")
```

### Control the scenes of your stream

Once identified, you can call the currently implemented functions documented in the [reference list](https://franklentz.github.io/onRobs/reference/index.html)

Once identified (see above), if you want to change the current scene of your stream, you can simply call :

```
# myobs is the websocket object created in the previous section
# the name of the scene must exist in OBS

# Change the scene of the stream to "BRB" (Be Right Back)
SetCurrentProgramScene(obs = myobs, sceneName  = "BRB")

# Change the scene of the stream to "Muti Cam Scene"
SetCurrentProgramScene(obs = myobs, sceneName  = "Muti Cam Scene")


```



If you want to stop your interactions with OBS:

```
disconnectFromOBS(myobs)
```
