---
title: "ROBS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ROBS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, echo=FALSE}
knitr::opts_chunk$set(
	message = TRUE,
	warning = FALSE,
	include = FALSE
)
library(ROBS)
```


This package enables you to control OBS through the OBS Websockets Server.
Its strongly rely on the *websocket* package.

### OBS Websocket Server in OBS

OBS must be running (the package has been tested with version 29) and you need to start the websockets server.
You will find the websocket server in Tools > Websockets server Settings
Make sure 

### Connection and Identification

There are three steps to start interacting with OBS Webserver once it is running

- Create an OBSWebsocket (this is the object you will use to interact with OBS through the websockets server
- Establish a connection with the server
- Identify and authenticate. If authentication has been activated on the OBS Websockets server, you will need to supply the password

```
library(ROBS)
myobs <- createOBSWebsocket() 
connectToOBS(obs = myobs)
identifyToOBS(obs = myobs, eventSub = "33", password = "myObsWebsocketsServerPassword")
```
